%\documentclass[twocolumn]{article}
%\documentclass{article}
\documentclass[11pt,conference]{IEEEtran}
%\usepackage[cp1251]{inputenc}
%\usepackage[russian]{babel}
\usepackage[dvips]{graphicx}

\begin{document}
\title{Test data generation for arithmetic subsystem of CPUs \textsc{MIPS64}}
\author{Evgeni Kornikhin, CMC MSU}
\date{Moscow, 2008}

\maketitle

\begin{abstract}
%Рассматривается задача генерации тестовых данных для тестирования
%арифметической подсистемы центральных процессоров \textsc{MIPS64}.
%Для решения этой задачи предлагается метод, использующий формальное
%описание поведения процессора. Это описание предлагается делать на
%специализированном языке, допускающем автомаческое решение задачи.
The main problem is test data generation for arithmetic subsystem
testing of CPUs \textsc{MIPS64}. A method is proposed to solve this
problem. The method uses a formal description of processor
functionality. A language for this description is proposed also.
This language permits automatic test data generation.
\end{abstract}

%\section{Постановка задачи}
\section{Problem}
\input{problem}

%\section{Существующие методы}
\section{Existence methods}
\input{exists}

%\section{Текущие результаты}
\section{Current results}
\input{results}

%\section{Продолжение работы}
\section{Future works}
\input{future}

\begin{thebibliography}{XXX}
% ссылаться - \cite{AAA}
\bibitem{IEEEhowto:MIPS64} MIPS64 Architecture For Programmers VolumeII: The MIPS64 Instruction Set. Document Number: MD00087. Revision 2.00. June 9, 2003.
\bibitem{IEEEhowto:ECLiPSe} K.Apt, M.Wallace. Constraint Logic Programming using
Eclipse. Cambridge University Press, 2007.
\bibitem{IEEEhowto:CLP} K.Marriott, Peter.J.Stuckey. Programming with
Constraints. MIT Press, 1998.
%\bibitem{ALPS} K. Hatayamal, K. Hikonel, T. Miyazaki, H. Yamada.A Practical Approach to Instruction-Based Test Generation for Functional
%    Modules of VLSI Processors. VLSI Test Symposium, 1997., 15th
%    IEEE. Volume , Issue , 27 Apr-1 May 1997 pp. 17 - 22
%\bibitem{InKa} Gotlieb A., Botella B., Rueher M. A CLP Framework for Computing Structural Test Data // Proceedings of the First International Conference on Computational Logic, Springer-Verlag, 2000, pp. 399-413
\bibitem{IEEEhowto:ATPG} Richard D. Eldred: Test Routines Based on Symbolic Logical Statements. J. ACM 6(1): 33-37 (1959)
\bibitem{IEEEhowto:RTL} Davidson and Fraser; The Design and Application of a Retargetable Peephole Optimizer; ToPLaS v2(2) 191-202 (April 1980)
\bibitem{IEEEhowto:PathOriented} C.Paoli, M.-L. Nivet, J.-F.Santucci,
A.Campana. Electronic Design, Test and Applications, 2002.
Proceedings. The First IEEE International Workshop on Volume ,
Issue, 2002 Page(s):382 - 386
\bibitem{IEEEhowto:SAT-HDL} F.Fallah, S.Devadas, K.Keutzer. Functional Vector Generation For HDL Models Using Linear Programming and 3-Satisfiability // in Proceedings
 of the Design Automation Conference, pp. 528-533, June 1998.
\bibitem{IEEEhowto:GA-HDL} F.Corno, A.Manzone, A.Pincetti, M.Sonza Reorda, G.Squillero. Automatic Test Bench Generation for Validation of RT-level Descriptions: an Industrial Experience // DATE2000: Design, Automation and Test in Europe, Paris (F), March 2000, pp.
385-389.
\bibitem{IEEEhowto:LinearProg} R.Brinkmann, R.Drechsler. RTL-datapath verification using integer linear programming // In IEEE VLSI Design'01 \& Asia and South Pacific Design Automation Conference, Bangalore, pages 741--746, 2002.
\bibitem{IEEEhowto:cytron91efficiently} R.Cytron, J.Ferrante, B.K.Rosen, M.           N.Wegman, F.K.Zadeck. Efficiently Computing Static Single Assignment Form and the Control Dependence Graph // ACM Transactions on Programming Languages and Systems, vol.13, no.4, ACM Press, pp.451--490, 1991.
\end{thebibliography}

\end{document}
