\documentclass[conference]{IEEEtran}
%\documentclass[conference, 10pt]{IEEEtran}
%\usepackage[cp1251]{inputenc}
%\usepackage[russian]{babel}
%\usepackage{pscyr}
\usepackage{graphicx}
\usepackage{cite}

\begin{document}
\title{Test data generation for LRU cache-memory testing}

\author{\IEEEauthorblockN{Evgeni Kornikhin}
\IEEEauthorblockA{Moscow State University, Russia\\
Email: kornevgen@gmail.com} }


\maketitle


\begin{abstract}
System functional testing of microprocessors deals with many
assembly programs of given behavior. The paper proposes new
constraint-based algorithm of initial cache-memory contents
generation for given behavior of assembly program (with cache misses
and hits). Although algorithm works for any types of cache-memory,
the paper describes algorithm in detail for basis types of
cache-memory only: fully associative cache and direct mapped cache.
\end{abstract}

\input{intro}

\input{testtemplates}

\input{full}

\input{prm}

\input{common}

\section{Conclusion}
The paper devoted to the test data generation problem. Test data
contains initial contents of cache-memory. The paper has proposed
the constraint-based algorithm. Constraints consists of finite sets
variables and sets operations. Test data generation for fully
associative cache and direct mapped cache has been considered in
details. Proposed algorithm is used in projects of testing
MIPS-compatible microprocessors. ECLiPSe is used as constraint
solver.


\begin{thebibliography}{1}

\bibitem{IEEEhowto:kamkin}
A.S.~Kamkin, \emph{Test program generation for microprocessors}
// Proceedings of ISP RAS. \hskip 1em plus
  0.5em minus 0.4em\relax Vol. 14(2). P.23-64. 2008.

\bibitem{IEEEhowto:combinatorial}
K.~Takayama, F.~Fallah, \emph{A new functional test program
generation methodology} // Proceedings 2001 IEEE International
Conference on Computer Design: VLSI in Computers and Processors.
P.76–81. 2001.

\bibitem{IEEEhowto:ATPG}
F.~Ferrandi, D.~Sciuto, M.~Beardo, F.~Bruschi, \emph{An approach to
functional testing of vliw architectures} // Proceedings of the IEEE
International High-Level Validation and Test Workshop (HLDVT’00).
P.29–33. 2000.

\bibitem{IEEEhowto:GenesysPro}
Y.~Lichtenstein, M.~Rimon, M.~Vinov, M.~Behm, J.~Ludden,
\emph{Industrial experience with test generation languages for
processor verification} // Proceedings of the 41st Design Automation
Conference (DAC’04). 2004.

\end{thebibliography}




% that's all folks
\end{document}
